### 2017-06-18 src/problem.tex
fix errors

In the \todo{choose a name for the problem} VPN problem the goal is to find a
feasible embedding of a virtual path into the physical DAG that minimizes the
cost.

\begin{figure}[ht]
\centering
\scalebox{1}{
\input{fig-embedding}
}

>>>>

In the Service Chain Placement in SDN problem the goal is to find a
feasible embedding of a virtual path into the physical DAG that minimizes the
cost.

\begin{figure}[ht]
\centering
\scalebox{.8}{
\input{fig-embedding}
}
